Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
fixed

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Kimbee Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.

\subsubsection{Data Models}
  The server has three data models: recordings, children, and therapists. Recordings are the encoded microphone encodings and recognition data from the {\em Kimbee Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Kimbee Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child, and their token obtained from their {\em Kimbee Game} instance. Future recordings are then relayed to the therapist from this particular {\em Kimbee Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

\subsubsection{Audio Encoding \& Recording Storage}
  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone. This file is then compressed and stored into the database as a recording. The recognition data (whether the {\em Kimbee Game} instance thinks the recording was correct) and the target word are also stored with the recording model.

>>>>

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.

\subsubsection{Data Models}
  The server has three data models: recordings, children, and therapists. Recordings are the microphone encodings and recognition data from the {\em Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child, and their token obtained from their {\em Game} instance. Future recordings are then relayed to the therapist from this particular {\em Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

\subsubsection{Audio Encoding \& Recording Storage}
  When a audio file is recieved by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone. This file is then compressed and stored into the database as a recording. The recognition data (whether the {\em Game} instance thinks the recording was correct) and the target word are also stored with the recording model.
